---
title: "Argos_document"
subtitle: Cancer epidemiology
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(error = FALSE)
knitr::opts_chunk$set(message = FALSE)

library(dplyr)
outputFolder <- "C:/Users/youjin/Documents/project/output"
cancerList<-list(cohortId = c(1,2,3,4,5,6),
                 cohortName = c("colon", 'lung', 'stomach','breast','liver','thyroid'),
                 conceptIdSet = list(c(435754,443381,443382,443383,443384,443390,443391,4089661,4180790,4180791,4180792,4181344),              
                                     c(442139,4092217,4094876,4151250,4157333,258375),
                                     c(4149838,197803,4095320,4149837,4095319,4094856,4092061,443387,4095317),
                                     c(137809,4188544,4158563,4162253,4155292,4187850,4188545,432845),
                                     c(201519,4001171,4001172,4001664,4003021,4095432,4246127),
                                     c(4178976)) ,
                 
                 representConceptId = c())

```

# **Incidence Rate**

### Age Adjusted Incidence Rate according to Diagnosis Year
1. `r cancerList$cohortName[1]` cancer
![](`r file.path(outputFolder,paste0("incidence/",cancerList$cohortName[1],"CancerIncidencePropAgeAdj.png"))` )

```{r}
df <- read.csv(file.path(outputFolder,paste0("incidence/",cancerList$cohortName[1],"CancerIncidencePropAgeAdj.csv") ), header = TRUE)
colnames(df) <- gsub("X","",colnames(df))
df <- df[,-1]
knitr::kable(df)
```

2. `r cancerList$cohortName[2]` cancer
![](`r file.path(outputFolder,paste0("incidence/",cancerList$cohortName[2],"CancerIncidencePropAgeAdj.png"))` )

```{r}
df <- read.csv(file.path(outputFolder,paste0("incidence/",cancerList$cohortName[2],"CancerIncidencePropAgeAdj.csv") ), header = TRUE)
colnames(df) <- gsub("X","",colnames(df))
df <- df[,-1]
knitr::kable(df)
```

3. `r cancerList$cohortName[3]` cancer
![](`r file.path(outputFolder,paste0("incidence/",cancerList$cohortName[3],"CancerIncidencePropAgeAdj.png"))` )

```{r}
library(dplyr)
df <- read.csv(file.path(outputFolder,paste0("incidence/",cancerList$cohortName[3],"CancerIncidencePropAgeAdj.csv") ), header = TRUE)
colnames(df) <- gsub("X","",colnames(df))
df <- df[,-1]
knitr::kable(df)
```

4. `r cancerList$cohortName[4]` cancer
![](`r file.path(outputFolder,paste0("incidence/",cancerList$cohortName[4],"CancerIncidencePropAgeAdj.png"))` )

```{r}
library(dplyr)
df <- read.csv(file.path(outputFolder,paste0("incidence/",cancerList$cohortName[4],"CancerIncidencePropAgeAdj.csv") ), header = TRUE)
colnames(df) <- gsub("X","",colnames(df))
df <- df[,-1]
knitr::kable(df)
```

5. `r cancerList$cohortName[5]` cancer
![](`r file.path(outputFolder,paste0("incidence/",cancerList$cohortName[5],"CancerIncidencePropAgeAdj.png"))` )

```{r}
library(dplyr)
df <- read.csv(file.path(outputFolder,paste0("incidence/",cancerList$cohortName[5],"CancerIncidencePropAgeAdj.csv") ), header = TRUE)
colnames(df) <- gsub("X","",colnames(df))
df <- df[,-1]
knitr::kable(df)
```

6. `r cancerList$cohortName[6]` cancer
![](`r file.path(outputFolder,paste0("incidence/",cancerList$cohortName[6],"CancerIncidencePropAgeAdj.png"))` )

```{r}
library(dplyr)
df <- read.csv(file.path(outputFolder,paste0("incidence/",cancerList$cohortName[6],"CancerIncidencePropAgeAdj.csv") ), header = TRUE)
colnames(df) <- gsub("X","",colnames(df))
df <- df[,-1]
knitr::kable(df)
```

### Age Specified Incidence Rate according to Diagnosis Year
1. `r cancerList$cohortName[1]` cancer
![](`r file.path(outputFolder,paste0("incidence/",cancerList$cohortName[1],"CancerIncidencePropAgeAdj.png"))` )

```{r}
df <- read.csv(file.path(outputFolder,paste0("incidence/",cancerList$cohortName[1],"CancerIncidencePropAgeAdj.csv") ), header = TRUE)
colnames(df) <- gsub("X","",colnames(df))
df <- df[,-1]
knitr::kable(df)
```

2. `r cancerList$cohortName[2]` cancer
![](`r file.path(outputFolder,paste0("incidence/",cancerList$cohortName[2],"CancerIncidencePropAgeAdj.png"))` )

```{r}
df <- read.csv(file.path(outputFolder,paste0("incidence/",cancerList$cohortName[2],"CancerIncidencePropAgeAdj.csv") ), header = TRUE)
colnames(df) <- gsub("X","",colnames(df))
df <- df[,-1]
knitr::kable(df)
```

3. `r cancerList$cohortName[3]` cancer
![](`r file.path(outputFolder,paste0("incidence/",cancerList$cohortName[3],"CancerIncidencePropAgeAdj.png"))` )

```{r}
library(dplyr)
df <- read.csv(file.path(outputFolder,paste0("incidence/",cancerList$cohortName[3],"CancerIncidencePropAgeAdj.csv") ), header = TRUE)
colnames(df) <- gsub("X","",colnames(df))
df <- df[,-1]
knitr::kable(df)
```

4. `r cancerList$cohortName[4]` cancer
![](`r file.path(outputFolder,paste0("incidence/",cancerList$cohortName[4],"CancerIncidencePropAgeAdj.png"))` )

```{r}
library(dplyr)
df <- read.csv(file.path(outputFolder,paste0("incidence/",cancerList$cohortName[4],"CancerIncidencePropAgeAdj.csv") ), header = TRUE)
colnames(df) <- gsub("X","",colnames(df))
df <- df[,-1]
knitr::kable(df)
```

5. `r cancerList$cohortName[5]` cancer
![](`r file.path(outputFolder,paste0("incidence/",cancerList$cohortName[5],"CancerIncidencePropAgeAdj.png"))` )

```{r}
library(dplyr)
df <- read.csv(file.path(outputFolder,paste0("incidence/",cancerList$cohortName[5],"CancerIncidencePropAgeAdj.csv") ), header = TRUE)
colnames(df) <- gsub("X","",colnames(df))
df <- df[,-1]
knitr::kable(df)
```

6. `r cancerList$cohortName[6]` cancer
![](`r file.path(outputFolder,paste0("incidence/",cancerList$cohortName[6],"CancerIncidencePropAgeAdj.png"))` )

```{r}
library(dplyr)
df <- read.csv(file.path(outputFolder,paste0("incidence/",cancerList$cohortName[6],"CancerIncidencePropAgeAdj.csv") ), header = TRUE)
colnames(df) <- gsub("X","",colnames(df))
df <- df[,-1]
knitr::kable(df)
```

### Age Specified Incidence Rate according to Birth Cohort

```{r}
paste0()
```

# **Survival Rate**

### 1,3,5 year Survival Rate (Relative)

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
